---
title: "P8105_HW1_ah4028"
author: "Austin Hsin"
date: "2023-09-14"
output: html_document
---

Setup code to load `tidyverse` and `moderndive` libraries and to open the `early_january_weather` dataset.

```{r setup, message = FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(tidyverse)
library(moderndive)
data("early_january_weather") 
```

# Problem 1 

### Determining `early_january_weather` dataset details.

```{r, early_january_weather}
# Determining size of `early_january_weather` dataset with `nrow` and `ncol`
nrow(early_january_weather)

ncol(early_january_weather)

# Determining mean temperature of `early_january_weather` dataframe using variable `temp`
df = early_january_weather

mean(df$temp)
```
The dataset `early_january_weather` contains weather data from EWR (`origin`) between 01Sept2013 and 15Sept2013 and includes variables `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, and `time_hour`. 

There are 358 rows and 15 columns according to `nrow` and `ncol` respectively.

The mean temperature is 39.58212 degrees Fahrenheit.

### Creating a scatterplot of `temp`(y) vs. `time_hour`(x)

```{r, scatterplot}
# Scatterplot of `temp` vs `time_hour`, colored by `humid`
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

# Exporting scatterplot `temp` vs `time_hour` 
ggsave("early_january_weather_time_hour_by_temp.pdf", height = 4, width = 10)
```

The scatterplot shows that `time_hour` and `temp` have a positively correlated relationship such that as `time_hour` increases, `temp` increases.

## Problem 2

### Creating a data frame with specific variables and dimensions.

```{r, problem2_df}
# Set seed to ensure reproducibility
set.seed(123)

# Defining Data Frame
problem2_df = tibble(
  vec_numeric = rnorm(10, sd=1),
  vec_logical = vec_numeric > 0,
  vec_char = c("I", "am", "enjoying", "the", "data", "science", "course", "at", "Columbia", "immensely"),
  vec_factor = factor(rep(c("yes", "no", "maybe"), length = 10))
)
```

# Pulling vectors out of the dataframe to obtain their means

```{r, problem2_df means}
mean_vec_numeric = mean(pull(problem2_df, vec_numeric))
mean_vec_logical = mean(pull(problem2_df, vec_logical))
mean_vec_char = mean(pull(problem2_df, vec_char))
mean_vec_factor = mean(pull(problem2_df, vec_factor))
```

We are unable to pull the mean from `vec_char` and `vec_factor` because they do not contain numeric variables.

# Converting problem2_df vectors `vec_logical`, `vec_char`, and `vec_factor` to numeric variables

```{r, as_numeric, results=FALSE}
as.numeric(pull(problem2_df, vec_logical))
as.numeric(pull(problem2_df, vec_char))
as.numeric(pull(problem2_df, vec_factor))
```

Because `vec_logical` is true/false, `as.numeric` translates it to binary. With `vec_char`, the `as.numeric` is unable to translate the nominal data points and creates NA values as a result. Finally, with `vec_factor`, `as.numeric` is able to translate the levels into a 3 level categorical variable.