---
title: "P8105_HW1_ah4028"
author: "Austin Hsin"
date: "2023-09-14"
output: html_document
---

Setup code to include loading the moderndive library.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
```

## Problem 1

This is the code for loading the early_january_weather dataset and determining the details of the dataset.

```{r}
data("early_january_weather")
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
```

The dataset early_january_weather has variables origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. 

There are 358 rows and 15 columns according to nrow and ncol respectively.

The mean temperature is 39.6 degrees Fahrenheit.

## Problem 1 Plots

This is the code for plotting time_hour by temp, colored by humid, from the early_january_weather dataset.

```{r plots, echo=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("early_january_weather_time_hour_by_temp.pdf", height = 4, width = 6)
```


