---
title: "P8105_HW1_ah4028"
author: "Austin Hsin"
date: "2023-09-14"
output: html_document
---

Setup code to include loading the moderndive library.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
```

## Problem 1 Part 1

Code for loading the early_january_weather dataset and determining its details.

```{r, Problem 1 Part 1 - early_january_weather dataset}
#Loading early_january_weather dataset
data("early_january_weather") 

#Calling up early_january_weather dataset to determine variable list
early_january_weather

#Determining size of early_january_weather dataset with nrow and ncol
nrow(early_january_weather)

ncol(early_january_weather)

#Determining mean temperature of early_january_weather dataframe using variable temp
df = early_january_weather

mean(df$temp)
```

The dataset early_january_weather has variables origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. 

There are 358 rows and 15 columns according to nrow and ncol respectively.

The mean temperature is 39.58212 degrees Fahrenheit.

## Problem 1 Part 2

Code for plotting temp vs time_hour from early_january_weather dataset

```{r, Problem 1 Part 2}
#Scatterplot of temp vs time_hour, colored by humid
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

#Exporting scatterplot temp vs time_hour 
ggsave("early_january_weather_time_hour_by_temp.pdf", height = 4, width = 10)
```
I made the decision to divide Problem 1 into two different code chunks to neatly separate the discussion for the questions on the early_january_weather dataset and the plot of temp vs time_hour.

The scatterplot shows that as temperature rises, humidity decreases and that the temperature rises and falls with the day/night cycle.

